Defending Byzantine Attacks in Ensemble Federated Learning: A Reputation-based Phishing Approach

### 2022-03-01 Manuscript_TIFS/manuscript_TIFS.tex
03-01-earyly update
错误修改完成

\title{Defending Byzantine Attacks in Ensemble Federated Learning: A Reputation-based Phishing Approach}
\author{Beibei~Li,~\IEEEmembership{Member,~IEEE,}
        Peiran~Wang,~\IEEEmembership{Student Member,~IEEE,}
        Qinglei~Kong,~\IEEEmembership{Member,~IEEE,}
        Yuan~Zhang,~\IEEEmembership{Member,~IEEE,}
        and~Rongxing~Lu,~\IEEEmembership{Fellow,~IEEE}
\thanks{This paper is an extended version of the paper titled `FLPhish: Reputation-Based Phishing Byzantine Defense in Ensemble Federated Learning', which was published in IEEE ISCC 2021, and awarded `Best Paper'.}
\thanks{B. Li and P. Wang are with the School of Cyber Science and Engineering, Sichuan Universsity, Chengdu, Sichuan, China 610065. Email: libeibei@scu.edu.cn; wangpeiran@stu.scu.edu.cn.}
\thanks{Q. Kong is with the Future Network of Intelligence Institute, The Chinese University of Hong Kong, Shenzhen, China 518172, and also with The University of Science and Technology of China, Hefei, China 230052. Email: kql8904@163.com.}
\thanks{Y. Zhang is with the School of Computer Science and Engineering, University of Electronic Science and Technology of China, Chengdu, China 610054. Email: zy\_loye@126.com.}
\thanks{R. Lu is with the Faculty of Computer Science, University of New Brunswick, Fredericton, NB, Canada E3B 5A3. Email: rlu1@unb.ca.}
}

@@

\begin{abstract}
  Emerging as a promising distributed learning paradigm, federated learning (FL) has been widely adopted in many fields. Nonetheless, a big challenge for FL in real-world implementation is Byzantine attacks, where compromised clients can mislead or poison the training model by falsifying or manipulating the local model parameters. To solve this problem, in this paper, we present a reputation-based Byzantine robust-FL scheme (called FLPhish) for defending Byzantine attacks under the Ensemble Federated Learning architecture (called EFL). Specifically, we first develop a novel ensemble FL architecture, EFL, which allows FL compatible with different deep learning models in different clients. Second, we craft a phishing algorithm for the EFL architecture to identify possible Byzantine behaviors. Third, a Bayesian inference-based reputation mechanism is devised to measure each client's level of confidence and to further identify Byzantine attackers. Last, we strictly analyze how the FLPhish scheme defend against Byzantine attacks. Extensive experiments under different settings demonstrate that the proposed FLPhish achieves great efficacy in defending Byzantine attacks in EFL. FLPhish is tested with different fractions of Byzantine attackers and different degrees of distribution imbalance.
\end{abstract}

@@

\begin{table}[t]
  \caption{Summary of Notations}
  \resizebox{0.5\textwidth}{!}{
  \begin{tabular}{lp{6cm}}
    \bottomrule
    Term&Description\\
    \hline
    $s$ & central server in FL \\
    $c_i$ & the $i$th client in FL, $i=1,2,3,...,u$ \\
    $d_i$ & the local dataset preserved by the $i$th client \\
    $C$ & the ensemble of all the clients \\
    $u$ & the number of clients\\
    $D_t$ & the unlabeled dataset chosen by $s$ in each procedure\\
    $D$ & the unlabeled dataset preserved by $s$\\
    $n$ & the number of samples in $D_t$\\
    $B_t$ & the labeled dataset (\textit{`bait'}) chosen by $s$ in each procedure\\
    $B$ & the labeled dataset preserved by $s$\\
    $m$ & the number of samples in $B_t$\\
    $a_i^t$ & the accuracy of predictions of $B_t$ made by $c_i$ in $t$th procedure\\
    $q_i$ & the label of $c_i$ to judge it is a malicious client or not\\
    $r_q$ & the threhold of malicious clients\\
    $x^t_l$ & the $l$th data point in $D_t$\\
    $b_i$ & the Byzantine attacker\\
    $\sigma$ & the `trigger' in the backdoor attack\\
    $\iota$ & the backdoor label in the backdoor attack\\
    $\mathbf{M}$ & global model preserved by $s$\\
    $\mathbf{m_i}$ & local models trained by the $i$th client\\
    $\mathbf{k_i^t}$ & the predictions (\textit{`knowledge'}) made by the $i$th client in the $t$th procedure\\
    $\mathbf{\hat{y}^t_l}$ & the ensembled prediction of data point $x^t_l$\\
    $\mathbf{\hat{y}^i_l}$ & the prediction of $l$th data point made by $i$th client\\
    $\mathbf{K_t}$ & the aggregated labels (predictions) of the $t$th iteration's unlabeled dataset\\
    \hline
  \end{tabular}
  }
\end{table}

@@

\par Former researchers have offered certain Byzantine-robust techniques to deal with malicious Byzantine attackers under the FL application settings \cite{ref_12_defense,ref_13_defense,ref_15_defense,ref_16_defense,ref_17_defense,ref_28_defense,ref_29_defense,ref_30_defense,ref_31_defense,ref_32_defense}. Byzantine-robust techniques try to construct a global model with high accuracy in the presence of a finite number of malicious clients. According to their different mechanisms, we divide Byzantine-robust approaches into two major types. The first (named Byzantine-Detection) is based on the development of a Byzantine-robust aggregation algorithm that distinguishes suspected clients from benign clients. The suspected clients' gradient updates are subsequently removed from the aggregation process by the server. For instance, in the DRACO scheme proposed by Chen \textit{et al.}, each node analyzes duplicate gradients that the parameter server uses to mitigate the effects of adversarial updates \cite{ref_13_defense}. Another Byzantine-robust technique (named Byzantine-Tolerance) seeks to ensure that the aggregation process is tolerant to poisoned updates from Byzantine attackers without excluding Byzantine attackers. For example, in Median \cite{ref_16_defense}, the FL server sorts the values of each parameter and picks the median value of each parameter as the value to be utilized in global model updates. In this study, we provide a unique reputation-based phishing method (named FLPhish) to protect against Byzantine attacks in EFL. Our contributions are three-fold:
\begin{itemize}
  \item We design a new FL architecture, Ensemble Federated Learning (called EFL), which utilizes an unlabeled dataset to replace the gradient updates in typical FL. This architecture is more compatible with different deep learning models on different clients.
  \item We craft a `phishing' method based on EFL to detect Byzantine attacks. The `phishing' method employs an labeled dataset to detect the potential Byzantine attackers in the EFL architecture, which preserves the security of the EFL.
  \item We present a Bayesian inference-based reputation mechanism to promote FLPhish's aggregation. The reputation mechanism gives each client a reputation to measure its confidence value and identifies the clients with low reputation values as Byzantine attackers, which helps FLPhish identify the Byzantine attackers with higher accuracy.
\end{itemize}

\section{Related Work}
In this section, we discuss about the related research work about the proposed Byzantine defense methods in FL and the proposed reputation mechanism in cybersecurity research.
\subsection{Byzantine Defense Methods in Federated Learning}
Byzantine-robust schemes are very important for FL to enhance its security as Byzantine attacks can cause great damages to the FL system. Recent years have witnessed the increasing interest in the research of Byzantine-robust schemes in the context of FL. Most of the current Byzantine-robust FL methods tend to make a more robust aggregation rule which aims to tolerate the presence of Byzantine attackers. 
For example, in 2017, Chen \textit{et al.} developed an approach called Krum, which selects one client's update as a global model based on a square-distance score in each iteration \cite{ref_12_defense}.
In the same year, Blanchard \textit{et al}. proposed two Byzantine-tolerant FL aggregation rules called Trimmed mean and Median \cite{ref_16_defense}. Trimmed Mean considers each parameter of the model update individually. Trimmed Mean sorts the parameter of the model updates collected, and cuts off the largest ones and the smallest ones. Median sorts the values of each parameter of all local model updates as well. Besides it considers the median value of each parameter as the value of the parameter in the global model update. 
In 2018, Chen \textit{et al.} designed an approach called DRACO to evaluate redundant gradients that are used by the parameter server to eliminate the effects of adversarial updates. 
In 2019, Xie \textit{et al.} proposed Zeno, which uses a ranking-based preference mechanism \cite{ref_15_defense}. The server computes a score for each client by using the stochastic zero-order oracle. Then Zeno presents a ranking list of clients based on the estimated descent of the loss function and the magnitudes. At last, Zeno computes the global model update by aggregating the clients with the highest scores. 
In 2020, SLSGD developed by Xie \textit{et al.} also uses trimmed mean as the robust aggregation rules for Byzantine-robust FL \cite{ref_14_defense}. 
In the same year, Cao \textit{et al.} proposed a Byzantine-tolerant scheme: FLTrust to introduce the use of trust \cite{ref_17_defense}. In each iteration, the server calculates a trust score for each client at first and lowers the trust score if the client's local model update's direction deviates more from the direction of the global model update. The client with a trust score lower than the threshold is considered a malicious client.
In 2021, a privacy-enhanced FL (PEFL) framework is presented by Liu \textit{et al.}  \cite{ref_45_defense}. PEFL takes advantage of homomorphic encryption to protect the privacy of the clients. Furthermore, a channel using the effective gradient data extraction is provided for the server to punish poisoners.

@@

In this section, we discuss the system model, show the threat model and identify our design goals.

@@

\subsubsection{{FL Client}} The local dataset $d_i$ gathered by each FL client $c_i$ ($c_i$ denotes the $i$th client in FL) is preserved by each FL client $c_i$. The FL client $c_i$ uses its local dataset $d_i$ to update the model obtained from the FL server. The model gradient updates are then sent back to the FL server. Meanwhile, it repeats the preceding steps throughout the FL process until the FL server $s$ stops transmitting new models.

\subsection{Threat Model}
Byzantine attacks are a problem in the current system. We separate Byzantine attacks into two types according to the attack consequences:
\par \textit{1) Denial-of-Service Byzantine Attack:} In denial-of-service attacks, the Byzantine attackers intend to disturb the global model, thus making it produce wrong predictions of the normal dataset \cite{ref_04_model,ref_06_model,ref_07_data,yang2017generative,sun2018data}. The label flipping attack in the current system model can be used by a malicious Byzantine attacker $b_i$ to launch Byzantine attacks against the global model. Label flipping attacks require $b_i$ to change the labels of training data while ensuring that the data's features remain unchanged \cite{ref_18_label_flipping}. The local model of the Byzantine attacker, $b_i$ is trained with incorrect labels, resulting in a `poisoned' model with low accuracy. Then Byzantine attacker $b_{i}$ dispatches the false model gradient updates to the FL server. Therefore, the false model gradient updates cause the FL server to learn the false knowledge from clients. The server $s$'s aggregation process is performed on FedAvg, which takes each client $c_{i}$'s dataset $d_{i}$'s size as the aggregation weight for $c_{i}$. This means that a client $c_{i}$ with a larger size of $d_{i}$ gets a larger aggregation weight. Meanwhile, FedAvg takes the size of $d_{i}$ declared by $c_{i}$ as $d_{i}$'s real size, which means $b_{i}$ can declare a fake size value larger than $d_{i}$'s real size value to increase the impact of the attack. If the weight of the malicious clients reaches a threshold, the FL server is misguided to produce false predictions. 
\par In Section V, we first divided denial-of-service attacks into 2 types of attacks: The first one is the untargeted attack, which makes the Byzantine attackers change the labels of data samples from one type into another type (for instance, all the samples with label `5' are changed to label `0'). Another one is the random attack which makes the Byzantine attackers randomly change the label of data samples. Then we evaluated our framework against the 2 types of denial-of-service attacks.
\par \textit{2) Backdoor Byzantine Attack:} In backdoor attacks, called backdoor attacks, the disturbed global model will make wrong predictions of the data samples that have `backdoor' in them \cite{ref_08_data,ref_09_backdoor,ref_10_backdoor,ref_11_backdoor,ref_19_backdoor}. Backdoor attackers in FL need to embed some `triggers' (noted as $\sigma$) in their local dataset. Then they relabel the data samples with $\sigma$ as the target label $\iota$. Each backdoor attacker adopts the preprocessed local dataset with $\sigma$ to update the global model it received from the FL server. Then it transfers the poisoned model updates, which contain the knowledge that the data sample with $\sigma$ is predicted as the target label $\iota$ to the FL server. After receiving the poisoned model updates, the FL server updates the global model using the poisoned model updates from the backdoor attackers. After the update, the FL server's model misclassifies the data with the $\sigma$ to the target label $\iota$ of backdoor attackers. Take a backdoor attack process towards the construction of an FL on CIFAR-10 as an example. The backdoor attacker adds a grey square as $\sigma$ in each data sample. Each data sample with a $\sigma$ is labeled as `cat'. Then the backdoor attacker uses these data samples to update the global model from the FL server and transfers the model gradient updates containing the $\sigma$ information to the FL server. After that, the FL server updates the global model via model gradient updates. Thus, the global model learns the $\sigma$ information from the backdoor attacker. It misclassifies the data sample with the $\sigma$ as 'cat' as well.
\par In Section IV.D, we provide a theoretical analysis of how our FLPhish scheme can defend against backdoor Byzantine attacks.

\subsection{Design Goals}
The proposed FLPhish scheme's main goal is to provide a reliable method for accurately resisting opportunistic Byzantine attacks in our EFL architecture. The followings are our design goals:

\par \textit{1)} The typical FL design has several flaws, including incompatibility with various deep learning models in different clients and significant communication costs. As a result, we created EFL, a novel FL architecture inspired by the idea of ensemble learning. It lowers the cost of communication overhead and expands our ability to defend against Byzantine attacks in FL.
\par \textit{2)} The proposed EFL architecture currently needs a robust Byzantine attack protection mechanism. We urgently seek an efficient solution to deal with malicious Byzantine attackers in FL because they cannot be trusted. In our proposed EFL architecture, we describe a phishing-based approach to guard against Byzantine attacks.
\par \textit{3)} As the performance of each client remains not stable in each iteration, it is important for our scheme to accurately measure each client's level of confidence in the long term. Therefore, we further propose an effective Bayesian inference-based reputation scheme based on our phishing-based model to spot Byzantine attacks compromised by malicious users.

\begin{figure*}
  \centering
\includegraphics[width=0.95\textwidth]{figures/Figure_FLPhish.pdf}
\caption{Our Proposed FLPhish Scheme.}
\label{fig_Phishing}
\end{figure*}

\section{Proposed FLPhish Scheme}
In this section, we show the proposed FLPhish scheme including the EFL architecture, the phishing mechanism, the reputation mechanism, and the security analysis of Byzantine attacks.

@@

\begin{algorithm}[t]
\caption{KnowledgeEnsemble} %algorithm name
\label{alg:KnowledgeEnsemble}
\hspace*{0.02in} {\bf Input:} %input of the algorithm
the ensemble of each client's prediction (`distilled knowledge') ${\mathbf{k_i^t}}_{\left \{ i= 1,2,3,...,u \right \}}$; the size of each client's local dataset ${e_i}_{\left \{ i= 1,2,3,...,u \right \}}$; the unlabeled dataset $D_t$ used in $t$th iteration; $\mathbf{\hat{y}^t}$ is the ensembled prediction of dataset $D_t$; $\mathbf{\hat{y}^t_l}$ denotes the prediction of the dataset $D_t$ made by $i$th client;\\
\hspace*{0.02in} {\bf Output:} %output of the algorithm
\begin{algorithmic}[1]
  \For{$l=1,2,3,...,n$ ($l=1,2,3,...,n$, denotes the data point in the unlabeled dataset)}
    \State $\mathbf{\hat{k}^t}$ $\gets$ $\sum_{i=1}^{u}\frac{e_i}{\sum_{i=1}^{u}e_i}\mathbf{\hat{k}^t}_i$;
    \State $\mathbf{\hat{y}^t}\gets argmax(\mathbf{\hat{k}^t})$;
  \EndFor \\
  \Return $\mathbf{\hat{y}^t}$.
\end{algorithmic}

\end{algorithm}

\subsection{Designed Ensemble Federated Learning}
Inspired by ensemble learning, we propose a new FL architecture, called EFL.
\par Typical FL architecture collects FL clients' model gradient updates, and aggregates them for the global model updates. Unlike them, our proposed FLPhish scheme applies an unlabeled dataset (the FL server preserves this dataset, while does not have its label or lacks enough resources to get its label) preserved by the FL server and all the clients' predictions of this dataset for global model updates.
\subsubsection{{FL Client}} Each FL client {$c_{i}$} ($i$ denotes the client's serial number) collects and labels its local data from various data sources to build its local dataset. Then, {$c_{i}$} uses the local dataset to train its local model. When {$c_{i}$} receives a public dataset from the FL server in each iteration, it uses its local model to produce predictions for the dataset and sends the predictions back to the FL server $s$.
\subsubsection{{FL Server}} The public dataset and the global model are built and preserved by the FL server $s$. The public dataset is made up of unlabeled data that the FL server does not have labels for it. $s$ either collects data from other data sources or generates data by itself to build the public dataset. In each iteration, the public dataset is transmitted to each client by the FL server $s$ after its construction. Each client $c_i$ uses its local model preserved by itself to make predictions about the public dataset and sends the prediction results back to $s$. After getting all of the predictions from all of the customers, $s$ aggregates them into a single set of predictions
\begin{equation}
\mathbf{\hat{k}^t}=\sum_{i=1}^{u}\frac{e_i}{\sum_{i=1}^{u}e_i}\mathbf{\hat{k}^t}_i.
\end{equation}
Then the FL server $s$ utilizes the aggregated predictions $\mathbf{\hat{k}^t}$ to compute the aggregated labels
\begin{equation}
\mathbf{\hat{y}^t}\gets argmax(\mathbf{\hat{k}^t}).
\end{equation} 
Then the FL server {$s$} employs the public dataset and the aggregated labels as the dataset's labels to update the global model.

@@

\subsection{Experiment Setup}

>>>>

\title{Defending Byzantine Attacks in Ensemble Federated Learning: A Reputation-based Phishing Approach}
\author{Beibei~Li,~\IEEEmembership{Member,~IEEE,}
        Peiran~Wang,~\IEEEmembership{Student Member,~IEEE,}
        Qinglei~Kong,~\IEEEmembership{Member,~IEEE,}
        Yuan~Zhang,~\IEEEmembership{Member,~IEEE,}
        and~Rongxing~Lu,~\IEEEmembership{Fellow,~IEEE}
\thanks{This paper is an extended version of the paper titled `FLPhish: Reputation-Based Phishing Byzantine Defense in Ensemble Federated Learning', which was published in 26th IEEE Symposium on Computers and Communications (ISCC 2021), and awarded \textbf{`Best Paper'}.}
\thanks{B. Li and P. Wang are with the School of Cyber Science and Engineering, Sichuan Universsity, Chengdu, Sichuan, China 610065. Email: libeibei@scu.edu.cn; wangpeiran@stu.scu.edu.cn.}
\thanks{Q. Kong is with the Future Network of Intelligence Institute, The Chinese University of Hong Kong, Shenzhen, China 518172, and also with The University of Science and Technology of China, Hefei, China 230052. Email: kql8904@163.com.}
\thanks{Y. Zhang is with the School of Computer Science and Engineering, University of Electronic Science and Technology of China, Chengdu, China 610054. Email: zy\_loye@126.com.}
\thanks{R. Lu is with the Faculty of Computer Science, University of New Brunswick, Fredericton, NB, Canada E3B 5A3. Email: rlu1@unb.ca.}
}

@@

\begin{abstract}
  Emerging as a promising distributed learning paradigm, federated learning (FL) has been widely adopted in many fields. Nonetheless, a big challenge for FL in real-world implementation is Byzantine attacks, where compromised clients can mislead or poison the training model by falsifying or manipulating the local model parameters. To solve this problem, in this paper, we present a reputation-based Byzantine robust-FL scheme (called FLPhish) for defending Byzantine attacks under the Ensemble Federated Learning architecture (called EFL). Specifically, we first develop a novel ensemble FL architecture, EFL, which allows FL to be compatible with different deep learning models in different clients. Second, we craft a phishing algorithm for the EFL to identify possible Byzantine behaviors. Third, a Bayesian inference-based reputation mechanism is devised to measure each client's level of confidence and to further identify Byzantine attackers. Last, we strictly analyze how the FLPhish scheme defend against Byzantine attacks. Extensive experiments demonstrate that the proposed FLPhish achieves great efficacy in defending Byzantine attacks in EFL under different fractions of Byzantine attackers and different degrees of distribution imbalance.
\end{abstract}

@@

\begin{table}[t]
  \caption{Summary of Notations}
  \resizebox{0.5\textwidth}{!}{
  \begin{tabular}{lp{6cm}}
    \bottomrule
    Term&Description\\
    \hline
    $s$ & central server in FL \\
    $c_i$ & the $i$ th client in FL, $i=1,2,3,...,u$ \\
    $d_i$ & the local dataset preserved by the $i$ th client \\
    $C$ & the ensemble of all the clients \\
    $u$ & the number of clients\\
    $D_t$ & the unlabeled dataset chosen by $s$ in each iteration\\
    $D$ & the unlabeled dataset preserved by $s$\\
    $n$ & the number of samples in $D_t$\\
    $B_t$ & the labeled dataset chosen by $s$ in each iteration\\
    $B$ & the labeled dataset preserved by $s$\\
    $m$ & the number of samples in $B_t$\\
    $a_i^t$ & the accuracy of predictions of $B_t$ made by $c_i$\\
    $q_i$ & the label of $c_i$ to judge it is a malicious client or not\\
    $r_q$ & the threhold of malicious clients\\
    $x^t_l$ & the $l$ th data point in $D_t$\\
    $b_i$ & the Byzantine attacker\\
    $\sigma$ & the `trigger' in the backdoor attack\\
    $\iota$ & the backdoor label in the backdoor attack\\
    $\mathbf{M}$ & global model preserved by $s$\\
    $\mathbf{m_i}$ & local models trained by the $i$ th client\\
    $\mathbf{k_i^t}$ & the predictions of the $i$ th client in the $t$ th iteration\\
    $\mathbf{\hat{y}^t_l}$ & the ensembled prediction of data point $x^t_l$\\
    $\mathbf{\hat{y}^i_l}$ & the prediction of $l$ th data point made by $i$ th client\\
    $\mathbf{K_t}$ & the aggregated labels of $D_t$\\
    \hline
  \end{tabular}
  }
\end{table}

@@

\par Former researchers have offered certain Byzantine-robust techniques to deal with malicious Byzantine attackers under the FL application settings \cite{li2021flphish, ref_12_defense,ref_13_defense,ref_15_defense,ref_16_defense,ref_17_defense,ref_28_defense,ref_29_defense,ref_30_defense,ref_31_defense,ref_32_defense}. Byzantine-robust techniques try to construct a global model with high accuracy in the presence of a finite number of malicious clients. According to their different mechanisms, we divide Byzantine-robust approaches into two major types. The first (named Byzantine-Detection) is based on the development of a Byzantine-robust aggregation algorithm that distinguishes suspected clients from benign clients. The suspected clients' gradient updates are subsequently removed from the aggregation process by the server. For instance, in the DRACO scheme proposed by Chen \textit{et al.}, each node analyzes duplicate gradients that the parameter server uses to mitigate the effects of adversarial updates \cite{ref_13_defense}. Another Byzantine-robust technique (named Byzantine-Tolerance) seeks to ensure that the aggregation process is tolerant to poisoned updates from Byzantine attackers without excluding Byzantine attackers. For example, in Median \cite{ref_16_defense}, the FL server sorts the values of each parameter and picks the median value of each parameter as the value to be utilized in global model updates. We have also studied the problem of Byzantine defense, and this study is the extensive version of our previous work \cite{li2021flphish}. In this study, we provide a unique reputation-based phishing method (named FLPhish) to protect against Byzantine attacks in EFL. Our contributions are three-fold:
\begin{itemize}
  \item We design a new FL architecture, Ensemble Federated Learning (called EFL), which utilizes an unlabeled dataset to replace the gradient updates in typical FL. This architecture is more compatible with different deep learning models on different clients.
  \item We craft a `phishing' method based on EFL to detect Byzantine attacks. The `phishing' method employs an labeled dataset to detect the potential Byzantine attackers in the EFL, which preserves the security of the EFL.
  \item We present a Bayesian inference-based reputation mechanism to promote FLPhish's aggregation. The reputation mechanism gives each client a reputation to measure its confidence value and identifies the clients with low reputation values as Byzantine attackers, which helps FLPhish identify the Byzantine attackers with higher accuracy.
\end{itemize}

\section{Related Work}
In this section, we introduce the related research work about the proposed Byzantine defense methods in FL and the proposed reputation mechanism in cybersecurity research.
\subsection{Byzantine Defense Methods in Federated Learning}
Byzantine-robust schemes are very important for FL to enhance its security as Byzantine attacks can cause great damages to the FL system. Recent years have witnessed the increasing interest in the research of Byzantine-robust schemes in the context of FL. Most of the current Byzantine-robust FL methods tend to make a more robust aggregation rule which aims to tolerate the presence of Byzantine attackers. 
For example, in 2017, Chen \textit{et al.} developed an approach called Krum, which selects one client's update as a global model based on a square-distance score in each iteration \cite{ref_12_defense}.
In the same year, Blanchard \textit{et al}. proposed two Byzantine-tolerant FL aggregation rules called Trimmed mean and Median \cite{ref_16_defense}. Trimmed Mean considers each parameter of the model update individually. Trimmed Mean sorts the parameter of the model updates collected, and cuts off the largest ones and the smallest ones. Median sorts the values of each parameter of all local model updates as well. Besides it considers the median value of each parameter as the value of the parameter in the global model update. 
In 2018, Chen \textit{et al.} designed an approach called DRACO to evaluate redundant gradients that are used by the parameter server to eliminate the effects of adversarial updates. 
In 2019, Xie \textit{et al.} proposed Zeno, which uses a ranking-based preference mechanism \cite{ref_15_defense}. The server computes a score for each client by using the stochastic zero-order oracle. Then Zeno presents a ranking list of clients based on the estimated descent of the loss function and the magnitudes. At last, Zeno computes the global model update by aggregating the clients with the highest scores. 
In 2020, SLSGD developed by Xie \textit{et al.} also uses trimmed mean as the robust aggregation rules for Byzantine-robust FL \cite{ref_14_defense}. 
In the same year, Cao \textit{et al.} proposed a Byzantine-tolerant scheme: FLTrust to introduce the use of trust \cite{ref_17_defense}. In each iteration, the server calculates a trust score for each client at first and lowers the trust score if the client's local model update's direction deviates more from the direction of the global model update. The client with a trust score lower than the threshold is considered a malicious client.
In 2021, a privacy-enhanced FL (PEFL) framework is presented by Liu \textit{et al.}  \cite{ref_45_defense}. PEFL takes advantage of homomorphic encryption to protect the privacy of the clients. Furthermore, a channel using the effective gradient data extraction is provided for the server to punish poisoners.

@@

In this section, we elaborate on the system model, show the threat model and identify our design goals.

@@

\subsubsection{{FL Client}} The local dataset $d_i$ gathered by each FL client $c_i$ ($c_i$ denotes the $i$ th client in FL) is preserved by each FL client $c_i$. The FL client $c_i$ uses its local dataset $d_i$ to update the model obtained from the FL server. The model gradient updates are then sent back to the FL server. Meanwhile, it repeats the preceding steps throughout the FL process until the FL server $s$ stops transmitting new models.

\subsection{Threat Model}
Byzantine attacks are a problem in the current system. We separate Byzantine attacks into two types according to the attack consequences:
\par \textit{1) Denial-of-Service Byzantine Attack:} In denial-of-service attacks, the Byzantine attackers intend to disturb the global model, thus making it produce wrong predictions of the normal dataset \cite{ref_04_model,ref_06_model,ref_07_data,yang2017generative,sun2018data}. The label flipping attack in the current system model can be used by a malicious Byzantine attacker $b_i$ to launch Byzantine attacks against the global model. Label flipping attacks require $b_i$ to change the labels of training data while ensuring that the data's features remain unchanged \cite{ref_18_label_flipping}. The local model of the Byzantine attacker, $b_i$ is trained with incorrect labels, resulting in a `poisoned' model with low accuracy. Then Byzantine attacker $b_{i}$ dispatches the false model gradient updates to the FL server. Therefore, the false model gradient updates cause the FL server to learn the false knowledge from clients. The server $s$'s aggregation process is performed on FedAvg, which takes each client $c_{i}$'s dataset $d_{i}$'s size as the aggregation weight for $c_{i}$. This means that a client $c_{i}$ with a larger size of $d_{i}$ gets a larger aggregation weight. Meanwhile, FedAvg takes the size of $d_{i}$ declared by $c_{i}$ as $d_{i}$'s real size, which means $b_{i}$ can declare a fake size value larger than $d_{i}$'s real size value to increase the impact of the attack. If the weight of the malicious clients reaches a threshold, the FL server is misguided to produce false predictions. 
\par We divided denial-of-service attacks into 2 types of attacks: The first one is the untargeted attack, which makes the Byzantine attackers change the labels of data samples from one type into another type (for instance, all the samples with label `5' are changed to label `0'). Another one is the random attack which makes the Byzantine attackers randomly change the label of data samples.
\par \textit{2) Backdoor Byzantine Attack:} In backdoor attacks, called backdoor attacks, the disturbed global model will make wrong predictions of the data samples that have `backdoor' in them \cite{ref_08_data,ref_09_backdoor,ref_10_backdoor,ref_11_backdoor,ref_19_backdoor}. Backdoor attackers in FL need to embed some `triggers' (noted as $\sigma$) in their local dataset. Then they relabel the data samples with $\sigma$ as the target label $\iota$. Each backdoor attacker adopts the preprocessed local dataset with $\sigma$ to update the global model it received from the FL server. Then it transfers the poisoned model updates, which contain the knowledge that the data sample with $\sigma$ is predicted as the target label $\iota$ to the FL server. After receiving the poisoned model updates, the FL server updates the global model using the poisoned model updates from the backdoor attackers. After the update, the FL server's model misclassifies the data with the $\sigma$ to the target label $\iota$ of backdoor attackers. Take a backdoor attack process towards the construction of an FL on CIFAR-10 as an example. The backdoor attacker adds a grey square as $\sigma$ in each data sample. Each data sample with a $\sigma$ is labeled as `cat'. Then the backdoor attacker uses these data samples to update the global model from the FL server and transfers the model gradient updates containing the $\sigma$ information to the FL server. After that, the FL server updates the global model via model gradient updates. Thus, the global model learns the $\sigma$ information from the backdoor attacker. It misclassifies the data sample with the $\sigma$ as 'cat' as well.

\subsection{Design Goals}
The proposed FLPhish scheme's main goal is to provide a reliable method for accurately resisting opportunistic Byzantine attacks in our EFL. The followings are our design goals:

\par \textit{1)} The typical FL design has several flaws, including incompatibility with various deep learning models in different clients and significant communication costs. As a result, we created EFL, a novel FL architecture inspired by the idea of ensemble learning. It lowers the cost of communication overhead and expands our ability to defend against Byzantine attacks in FL.
\par \textit{2)} The proposed EFL currently needs a robust Byzantine attack protection mechanism. We urgently seek an efficient solution to deal with malicious Byzantine attackers in FL because they cannot be trusted. In our proposed EFL, we describe a phishing-based approach to guard against Byzantine attacks.
\par \textit{3)} As the performance of each client remains not stable in each iteration, it is important for our scheme to accurately measure each client's level of confidence in the long term. Therefore, we further propose an effective Bayesian inference-based reputation scheme based on our phishing-based model to spot Byzantine attacks compromised by malicious users.

\begin{figure*}
  \centering
\includegraphics[width=0.95\textwidth]{figures/Figure_FLPhish.pdf}
\caption{The Proposed FLPhish Scheme.}
\label{fig_Phishing}
\end{figure*}

\section{The Proposed FLPhish Scheme}
In this section, we show the proposed FLPhish scheme including the EFL, the phishing mechanism, the reputation mechanism, and the security analysis of Byzantine attacks.

@@

\begin{algorithm}[t]
  \caption{KnowledgeEnsemble$(\mathbf{k_1^t},\mathbf{k_2^t},\mathbf{k_3^t},...,\mathbf{k_u^t})$} %algorithm name
  \label{alg:KnowledgeEnsemble}
  \hspace*{0.02in} {\bf Input:} %input of the algorithm
  the ensemble of each client's prediction (`distilled knowledge') ${\mathbf{k_i^t}}_{\left \{ i= 1,2,3,...,u \right \}}$; the size of each client's local dataset ${e_i}_{\left \{ i= 1,2,3,...,u \right \}}$; the unlabeled dataset $D_t$ used in $t$ th iteration; $\mathbf{\hat{y}^t}$ is the ensembled prediction of dataset $D_t$; $\mathbf{\hat{y}^t_l}$ denotes the prediction of the dataset $D_t$ made by $i$ th client;\\
  \hspace*{0.02in} {\bf Output:} %output of the algorithm
  \begin{algorithmic}[1]
    \For{$l=1,2,3,...,n$ ($l=1,2,3,...,n$, denotes the data point in the unlabeled dataset)}
      \State $\mathbf{\hat{k}^t}$ $\gets$ $\sum_{i=1}^{u}\frac{e_i}{\sum_{i=1}^{u}e_i}\mathbf{\hat{k}^t}_i$;
      \State $\mathbf{\hat{y}^t}\gets argmax(\mathbf{\hat{k}^t})$;
    \EndFor \\
    \Return $\mathbf{\hat{y}^t}$.
  \end{algorithmic}
  \end{algorithm}

\subsection{The Designed Ensemble Federated Learning}
\par Typical FL architecture collects FL clients' model gradient updates, and aggregates them for the global model updates. Inspired by ensemble learning, we propose a new FL architecture, called EFL. Unlike them, our proposed EFL applies an unlabeled dataset (the FL server preserves this dataset, while does not have its label or lacks enough resources to get its label) preserved by the FL server and all the clients' predictions of this dataset for global model updates.
\subsubsection{{FL Client}} Each FL client {$c_{i}$} ($i$ denotes the client's serial number) collects and labels its local data from various data sources to build its local dataset. Then, {$c_{i}$} uses the local dataset to train its local model. When {$c_{i}$} receives a public dataset from the FL server in each iteration, it uses its local model to produce predictions for the dataset and sends the predictions back to the FL server $s$.
\subsubsection{{FL Server}} The public dataset and the global model are built and preserved by the FL server $s$. The public dataset is made up of unlabeled data that the FL server does not have labels for it. $s$ either collects data from other data sources or generates data by itself to build the public dataset. In each iteration, the public dataset is transmitted to each client by the FL server $s$ after its construction. Each client $c_i$ uses its local model preserved by itself to make predictions about the public dataset and sends the prediction results back to $s$. After getting all of the predictions from all of the customers, $s$ aggregates them into a single set of predictions
\begin{equation}
\mathbf{\hat{k}^t}=\sum_{i=1}^{u}\frac{e_i}{\sum_{i=1}^{u}e_i}\mathbf{\hat{k}^t}_i.
\end{equation}
Then the FL server $s$ utilizes the aggregated predictions $\mathbf{\hat{k}^t}$ to compute the aggregated labels
\begin{equation}
\mathbf{\hat{y}^t}\gets argmax(\mathbf{\hat{k}^t}).
\end{equation} 
Then the FL server {$s$} employs the public dataset and the aggregated labels as the dataset's labels to update the global model.

@@

\subsection{Experiment Settings}
